Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex
Finished up my sections

\Section{Case Company Description}
TBA

@@

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Company X tackle the problems related to the research questions has been the most central part of the study. Because of the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting. This line of thought is supported by Runesson \& Höst in CITE XXX. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies CITE XXX.

During the initial stage of the study, careful planning was conducted. The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning was related to communicating with Company X to facilitate the interviews. A time-line for the interviews was created and established with company X. The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.

\SubSection{Preparation for Data Collection}
During this stage the interviews were designed. The initial design of the interview was pilot tested on three employees of Company X. The results from the pilot tests were used to test if the interviews would fulfil the objective of the study. The number of subjects for the main interviews was 15. They were sampled randomly from employment records at Company X.

During this stage, all ethical precautions of the study were taken. It was established that Company X wanted to remain anonymous and that all interviews must happen on a voluntary basis. An agreement on to what extent Company X's documentation could be used was also made during this stage.
%Add what was agreed

\SubSection{Data Gathering}
The data has mainly been gathered through first degree interviews CITE LETHBRIDGE 2005 XXX. The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents. Data triangulation was performed to compare and verify the results based on which role the interviewee had. The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes. The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach. The fact that the interviewees had widely differing backgrounds and roles was the main reason for not using a structured approach. A semi-structured approach was chosen over a unstructured approach to be able to obtain results which were closely related to each other. This was performed so that meaningful comparison and analysis could be carried out. Company X's change process documentation was also analysed to provide further depth to the analysis already performed. Please see Appendix A for a full list of interview questions.

@@

\begin{itemize}
\item Create questions for your interviews (include the questions in your report)
\item Discuss validity threats
\item Triangulation = counteract research bias
\item In meth, mention how the interviewees were selected and contacted (you have a gatekeeper which selects the people for you)
\item Mention how many of each role and why each role was included (triangulation)
\item convenience sampling (yo uhave contact at company already and use them) and maximum variation (i aim to have as many as possible)
\item Mention how the company was selected and what the criteria was (there was some lazy w)
\item the documents analysis (triangulation) will mostly be used to verify what the change agents say
\end{itemize}

>>>>

@@

\SubSection{Case Company Description}
The subject case organisation in this study is Ericsson. Ericsson operates in the domain of communications technology, and their main products are in the domain of mobility, broadband and cloud-based services \cite{a7} \cite{a8}. Ericsson has 117,508 employees (as of September 30, 2014), 25,300 of which work in R\&D (Research and Development). \cite{a7}.

Our research has been conducted at the Evolved Packet Gateway (EPG) department of Ericsson. The EPG department consists of approximately 700 employees, the majority of hwich work on software development related tasks. EPG delivers and maintains the EPG product which is a part of Ericsson's product for deployment of Long Term Evolution (LTE) networks \cite{a9}. The EPG product serves as a gateway between Ericsson's packet core network and other packet data networks, such as the Internet \cite{a9}. The EPG product is utilized in technologies such as 2G, 2G+, 3G, 4G and Wi-Fi hotspots \cite{a9}.

The company was sampled through convenience sampling, and a maximum varation strategy was used. As such, the goal was to include as many companies as possible in this study. Since the study is conducted at a large communications technology company, it indicates that the study may be generalisable to similar companies.

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the most central part of the study. Because of the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}.

During the initial stage of the study, careful planning was conducted. The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning was related to communicating with Ericsson to facilitate the interviews. A time-line for the interviews was created and established with Ericsson. The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.

\SubSection{Preparation for Data Collection}
The interviewees were sampled using random sampling, with help of a gatekeeper at the company. The reason a gatekeeper was used was to reduce research bias. The random sampling was done on official employee records. The number of subjects for the interviews was (XXX or were?) 15. The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents, and 5 of each role were interviewed. The main reason the three different roles were included was to be able to reduce reserach bias through data triangulation.

The interviewees were selected based on two criterion: they must have been employed at Ericsson for a minimum of 5 years and they must work at the EPG department. 5 years expirence was set as a minimum to ensure that all interviewees had experienced a fair number of changes at Ericsson. The reason only employees from EPG were accepted was to ensure that the population was cohesive.

During this stage, all ethical precautions of the study were taken. It was established that Ericsson did not require anonymity and that all interviews must happen on a voluntary basis. An agreement that Ericsson's change process documentation could be used as a data source in the study was also made.

\SubSection{Data Gathering}
The data has mainly been gathered through first degree interviews \cite{lethbridge2005studying}. The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach. The fact that the interviewees had widely differing backgrounds and roles was the main reason for not using a structured approach. A semi-structured approach was chosen over a unstructured approach to be able to obtain results which were closely related to each other. This was performed so that meaningful comparison and analysis could be carried out. Data triangulation was performed to compare and verify the results based on which role the interviewee had. The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes.

Ericsson's change process documentation was also analysed to provide further depth to the analysis already performed. The documentation was also used to triangulate the interview answers that related to Ericsson's change strategy. The reason for was to reduce risks of research bias. Please see Appendix A (XXX or 1?) for a full list of interview questions.

@@

\begin{itemize}
\item Create questions for your interviews (include the questions in your report)
\item Mention how the company was selected and what the criteria was (there was some lazy w)
\end{itemize}
